Statistical Stopping Criteria for Active Learning in Systematic Review Screening

### 2019-07-18 manuscript/main.tex
additional burden - scrape review

		\begin{fmbox}
			\dochead{Research}

@@

			\begin{abstract} % abstract
				\parttitle{First part title} %if any
				Active learning for systematic review screening promises to reduce the human effort required to identify relevant documents for a systematic review. 
				Machines and humans  work together, with the human providing training data, and the machine optimising the documents a human screens. 
				However, current approaches lack robust stopping criteria, meaning that such systems are hard to implement in live reviews. 
				This paper introduces a workflow for working with robust and flexible statistical stopping criteria, that offer real work reductions on the basis of a given confidence level of reaching a given recall.

@@

			\begin{keyword}
				\kwd{sample}
				\kwd{article}
				\kwd{author}
			\end{keyword}

@@

	Figure \ref{sample-recall} shows the minimum estimated recall for a set of confidence intervals, along with the actual recall (in grey) for a case where 800 out of 2,000 documents have been reviewed, 2\% of remaining documents are relevant, and 20\% of all documents are relevant. We see that after 95\% recall has actually been achieved, but before 100\% of documents have been been seen, we can be confident at each of the given confidence levels that 95\% of relevant documents habe identified. All estimates of recall only reach 100\% after all documents have been seen, as it is not possible to exclude the possibility, at any given confidence level, that the proportion of relevant documents is greater than 0 \todo{Actually maybe this is possible if we work with whole numbers? How does that change things?}. Figure \ref{sample-recall-variation} shows the various trajectories of a 95\% minimum recall (blue) and actual recall (grey) given the same paramaters for 200 random samples.

@@

	In figure [], we investigate how the total number of documents and the proportion of relevant documents affect the additional burden \todo{Use the number of documents seen instead of p}.

@@

@@

>>>>

		\begin{fmbox}
			\dochead{Methodology}

@@

			\begin{abstract} % abstract
				%\parttitle{First part title} %if any
				Active learning for systematic review screening promises to reduce the human effort required to identify relevant documents for a systematic review. 
				Machines and humans  work together, with the human providing training data, and the machine optimising the documents a human screens. 
				However, current approaches lack robust stopping criteria, meaning that such systems are hard to implement in live reviews. 
				This paper introduces a workflow for working with robust and flexible statistical stopping criteria, that offer real work reductions on the basis of a given confidence level of reaching a given recall.

@@

			\begin{keyword}
				\kwd{Systematic Review}
				\kwd{Machine Learning}
				\kwd{Active Learning}
				\kwd{Stopping Criteria}
			\end{keyword}

@@

	Figure \ref{sample-recall} shows the minimum estimated recall for a set of confidence intervals, along with the actual recall (in grey) for a case where 800 out of 2,000 documents have been reviewed, 2\% of remaining documents are relevant, and 20\% of all documents are relevant. 
	We see that after 95\% recall has actually been achieved, but before 100\% of documents have been been seen, we can be confident at each of the given confidence levels that 95\% of relevant documents have been identified. 
	All estimates of recall only reach 100\% after all documents have been seen, as it is not possible to exclude the possibility, at any given confidence level, that the proportion of relevant documents is greater than 0 \todo{Actually maybe this is possible if we work with whole numbers? How does that change things?}. 
	Figure \ref{sample-recall-variation} shows the various trajectories of a 95\% minimum recall (blue) and actual recall (grey) given the same paramaters for 200 random samples.

@@

	In figure \ref{additional-burden}, we investigate how the total number of documents and the proportion of relevant documents affect the additional burden \todo{Use the number of documents seen instead of p?}. We demonstrate the additional burden decreases \todo{how? Non-linearly?} with increasing total numbers of documents. With decreasing relevance of the remaining documents (holding the recall constant at 95\%, this means that fewer documents remain unseen), the additional burden increases. This implies that where the machine learning has more successfully identified documents and reduced burden, the additional burden required to establish the level of recall is higher. This is because the proportion of documents not seen is greater, so uncertainty around the relevance of that proportion has a greater impact on the estimation of recall.

@@

	When to move to random sampling remains an open question. Our current approach is to use the predicted relevance of the machine learning model as a guide. We calculate the [minimum/maximum] estimated recall based on observing the predicted relevance level in [x] random documents. If the estimated recall would be below the threshold, then we begin drawing random documents.

	The stopping criteria explained here is

@@

	We evaluate each of the three criteria discussed on real world test data. With each method, we run 100 runs and record the recall error and actual work saved each time. We operationalise the heuristic stopping criteria with 10, 20, and 50 irrelevant records in a row. For simplicity, we use a basic SVM model [REFS], with 1-2 word n-grams in the document abstracts used as input data. We start with random samples of [100, 200, and 500] documents.
